%\documentclass{article}
%\usepackage[margin=1in]{geometry}
%\usepackage{graphicx}
%\usepackage{float}
%\begin{document}

\begin{itemize}
\item Uses GPS and ephemerides for position determination. Variable drag used to re-order satellites' in-track configuration \cite{Gangestad}.

\item Surveys various cubesat type propulsion systems and develops method for evaluating performance of these propulsion systems \cite{Spence}.

\item Describes approach to component selection and testing to meet the needs of cubesats \cite{Sinclair}.

\item Attitude determination for spinning spacecraft: uses sun sensor and RF Doppler measurment received at ground stations. Good for low cost, resource-limited spacecraft with moderate attitude determination requirement \cite{Tsuda}.

\item Cubesat attitude control system designed with sub-degree pointing accuracy using COTS miniature reaction wheels and a developmental micro-propulsion system \cite{Sanders}.

\item Precision attitude control (arc-second level), enabled by Blue Canyon Technologies Nano Star Camera-1 \cite{Palo}.

\item Semi-passive actuator where solar cells drive a small magnetic torquier automatically when illuminated. Applications in obtaining sun-avoiding attitudes \cite{Bonin}.

\item Error of attitude of star trackers are systematic. Methods of taking into account systematic error and decreasing effect on accuracy \cite{Tuchin}.

\item Attitude Determination and control system for 2-degree-accuracy surface track \cite{Aherne}.

\item Discusses antennas used in GNSS based precision orbit determination \cite{Zackrisson}.

\item Practical advice for handling and assembly of star trackers and discuss strategies for maximizing image quality over the sensor lifetime \cite{Enright}

\item Using reaction wheels and star tracker for ADCS \cite{Lemke}.

\item Development of a star tracker for CubeSat use \cite{Segert}.

\item An Off-the-shelf Electric Propulsion System for CubeSats \cite{Clark}.

\item Autonomous position and attitude determination of a swarm of satellites. Vision based system for attempting to dock. Attitude algorithms validated for distances up to 30 m and position determination tested for distances up to 50 m \cite{Smail}.

\item Uses active magnetic bearings to support and tilt a spinning rotor to provide 3-axis attitude control using a single actuator \cite{Seddon}.

\item Reaction wheel for 2 to 20 kg spacecraft. Wheel fits in 5x5x4cm box, weighs 185 g and consumes 100mW at nominal speed \cite{Sinclair2}.

\item Uses commercially available GPS receiver for orbit determination. RMS value of range error is 0.6m from flight data \cite{Saito}.

\item Low-cost visible imaging camera, radiation-hardened, 87x70x230 mm and ~0.6kg \cite{Shumway}.

\item SS-411 maintains mean accuracy of 0.16 deg over entire field of view \cite{Enright2}.

\item Optical based system that weighs less than 1 kg and consumes <3W. Spacecraft attitude to within 100 arc-seconds and angular rate information over rates up to 15 deg/sec \cite{Seng}.

\item Describes the Micro Sun Sensor (MSS), the result of the radiation test for commercial active pixel sensor and ground optical performance test of the MSS ground test model \cite{Yoshihara}.

\item Star Tracker 300 g, <1 W power, 100 arc-second or better pointing accuracy, pointing accuracies better than 0.25 degree \cite{Zenick}.

\item Attitude determination error of less than 1 degree from magnetometer and coarse sun sensor combination \cite{Theil}.
\end{itemize}


\begin{thebibliography}{99}
\bibitem{Gangestad} Gangestad, Joseph W., Brian S. Hardy, and David A. Hinkley. "Operations, Orbit Determination, and Formation Control of the AeroCube-4 CubeSats." 27th Annual AIAA/USU Conference on Small Satellites. 2013.
\bibitem{Spence} Spence, Douglas, et al. "Electrospray Propulsion Systems for Small Satellites." 27th Annual AIAA/USU Conference on Small Satellites. 2013.
\bibitem{Sinclair} Sinclair, Doug and Jonathan Dyer. "Radiation Effects and COTS Parts in SmallSats." 27th Annual AIAA/USU Conference on Small Satellites. 2013.
\bibitem{Tsuda} Tsuda, Yuichi, Takanao Saiki, and Yuya Mimasu. "Realization of Minimal Attitude Determination System for Small Spinner Spacecraft IKAROS." 27th Annual AIAA/USU Conference on Small Satellites. 2013.
\bibitem{Sanders} Sanders, Devon, et al. "Pushing the Limits of Cubesat Attitude Control: A Ground Demonstration." 27th Annual AIAA/USU Conference on Small Satellites. 2013.
\bibitem{Palo} Palo, Scott, George Stafford, and Alan Hoskins. "An Agile Multi-use Nano Star Camera for Constellation Applications." 27th Annual AIAA/USU Conference on Small Satellites. 2013.
\bibitem{Bonin} Bonin, Grant, et al. "The Torque Rudder: A Novel Semi-Passive Actuator for Small Spacecraft Attitude Control." 27th Annual AIAA/USU Conference on Small Satellites. 2013.
\bibitem{Tuchin} Tuchin, Maksim, et al. "On Random and Systematic Errors of a Star Tracker." 27th Annual AIAA/USU Conference on Small Satellites. 2013.
\bibitem{Aherne} Aherne, Michael, et al. "Aeneas -- Colony I meets Three-Axis Pointing." 25th Annual Conference on Small Satellites. 2011.
\bibitem{Zackrisson} Zackrisson, Jan and Mikael Ohgren. "GNSS Receive Antennas on Satellites for Precision Orbit Determination." 25th Annual Conference on Small Satellites. 2011.
\bibitem{Enright} Enright, John, Doug Sinclair, and Christy Fernando. "COTS Detectors for Nanosatellite Star Trackers: A Case Study." 25th Annual Conference on Small Satellites. 2011.
\bibitem{Lemke} Johnston-Lemke, B., et al. "Arc-Minute Attitude Stability on a Nanotsatellite: Enabling Stellar Photometry on the Smallest Scale." 25th Annual Conference on Small Satellites. 2011.
\bibitem{Segert} Segert, Tom, et al. "Development of the Pico Star Tracker ST-200 - Design Challenges and Road Ahead." 25th Annual Conference on Small Satellites. 2011.
\bibitem{Clark} Clark, Craig, et al. "An Off-the-shelf Electric Propulsion System for CubeSats." 25th Annual Conference on Small Satellites. 2011.
\bibitem{Smail} Smail, Samia, et al. "Autonomous Pose Estimations for In-Orbit Self-Assembly of Intelligent Self-Powered Modules." 23rd Annual Conference on Small Satellites. 2009.
\bibitem{Seddon} Seddon, Jon and Alexandre Pechev. "3Dwheel: 3-Axis Low Noise, High-Bandwidth Attitude Actuation from a Single Momentum Wheel Using Magnetic Bearings." 23rd Annual Conference on Small Satellites. 2009.
\bibitem{Sinclair2} Sinclair, Doug, C. Cordell Grant, and Robert Zee. "Enabling Reaction Wheel Technology for High Performance Nanosatellite Attitude Control." 21st Annual Conference on Small Satellites. 2007.
\bibitem{Saito} Saito, Hirobumi, et al. "Miniature Space GPS Receiver by means of Automobile-Navigation Technology." 21st Annual Conference on Small Satellites. 2007.
\bibitem{Shumway} Shumway, Andrew, et al. "Digital Imaging Space Camera (DISC) Design and Testing." 21st Annual Conference on Small Satellites. 2007.
\bibitem{Enright2} Enright, John and Doug Sinclair. "Algorithm Enhancements for the SS-411 Digital Sun Sensor." 21st Annual Conference on Small Satellites. 2007.
\bibitem{Seng} Seng, Bill, et al. "The AeroAstro Fast-Angular-Rate Miniature Star Tracker: Algorithms and Simulation Results." 19th Annual Conference on Small Satellites. 2005.
\bibitem{Yoshihara} Yoshihara, Keisuke, et al. "Micro Sun Sensor with CMOS Imager for Small Satellite Attitude Control." 19th Annual Conference on Small Satellites. 2005.
\bibitem{Zenick} Zenick, Ray and Thomas McGuire. "Lightweight, Low-Power Coarse Star Tracker." 17th Annual Conference on Small Satellites. 2003.
\bibitem{Theil} Theil, Stephan, Pontus Appel, and Alexander Schleicher. "Low Cost, Good Accuracy - Attitude Determination using Magnetometer and Simple Sun Sensor." 17th Annual Conference on Small Satellites. 2003.
\end{thebibliography}
%\end{document}